%!TEX root = thesis.tex


Getting to this point in one's academic career requires the help and support of dozens of people. I hope I can name you all. %Prepare yourself for some clich{\'e}s. 

First and foremost, I \textit{literally} would not be where I am today without my advisor, Claudia Scarlata. She unwittingly saved me from a life of drudging Statistics by asking me to join her research group moments before I was to accept the department transfer, and for this I am eternally grateful. I have the utmost respect for you as a researcher, a leader, a scientist, and a collaborator. Thank you for helping me gain the confidence in my abilities and myself without resorting to bullshit. Thank you for pushing me to finish what I start, as much as I may loathe it. And thank you for sticking with me even during our rockier moments. I would be honored to consider you not just my advisor and collaborator, but also my friend. 


For the past three years I've had the delightful fortune to be part of the Galaxy Zoo science team and the insight and guidance provided by collaborators Chris Lintott, Brooke Simmons, Karen Masters, Steven Bamford, and Becky Smethurst has been invaluable. Particular thanks go to Lucy Fortson as my unofficial co-adivsor. Thank you for your steady support, even hand, cool head, and constant (but gentle!) pressure.  You and Claudia make an amazing team and I am so grateful to have been part of it. 

Of course I am also indebted to the support provided by those within MIfA. Many thanks to Hugh Dickinson, John Phillips, Kyle Willett (ex-MIfA), Evan Skillman, and Terry J. Jones. Discussions with each of you helped shaped my research and my direction through graduate school in myriad, subtle ways. Finally, thanks to my additional committee members, Tom Jones and Yong Qian, for your expertise and time commitment. 


Obviously, no grad student is an island and I am so thankful that the grads in our program have always cared more for inclusion and camaraderie over advancement and competition. Thanks to all of you for the experiences that make grad school bearable: game nights, D\&D campaigns, roof beers, and camping trips. Thanks to my office mates Miceala Bagley and Vihang Mehta. You two have taught me more things and listened to me bitch more times than I can count. Thanks to Michael Gordon for Computer Club, for teaching me all the Pythons, and for daily hilarious stories. Thanks to my dancing buddy, Brian O'Neill; to my Dranks Club: Tony Young, Matt Gomer, and Trevor Knuth; to the best traveling partner one could hope for and without whom I could not be Melanie$^2$, Dr. Melanie Galloway; to Evan Tyler for relieving me of Outreach Coordinator duties (sorry, bro), and to Karlen Shahinyan. If you wait for Karlen, you die; but look who graduated first. 


Last but certainly not least, I couldn't have done this without all the support and love from my friends and family. Mom, thanks for letting me vent every Saturday morning. You never failed to cheer me on. And Max, thanks for helping me see (and believe!) what my skills are truly worth. PhD or GTFO. 


This work could not have been completed without the financial support of several institutions. In particular I am extremely grateful to the University of Minnesota Graduate School for both the Doctoral Dissertation Fellowship and the Thesis Research Travel Grant. Additionally, I am eternally indebted to the University of Oxford and New College, Oxford for the opportunity to conduct visiting research through the Balzan Fellowship. \\~



%%----------------------------------------------------------------------------------------------------------------------------------------------------
%%   ACKNOWLEDGEMENTS
%%----------------------------------------------------------------------------------------------------------------------------------------------------
\noindent Chapters 3 and 4 of this thesis are modified versions of a paper submitted to MNRAS. For flow and clarity, the acknowledgments for that paper are placed below. 

MB thanks Steven Bamford and Boris H{\"a}u{\ss}ler for insightful discussions on citizen science and Galaxy Zoo; and John Wallin and Marc Huertas-Company for several enlightening conversations on machine learning and classification. 
We are grateful to Elisabeth Baeten, Micaela Bagley, Karlen Shahinyan, Vihang Mehta, Steven Bamford, Kevin Schawinski, and Rebecca Smethurst for providing expert classifications in addition to those provided by the authors. PJM acknowledges Aprajita Verma and Anupreeta More for their ongoing collaboration on the Space Warps project. 

MB, CS, LF, KW, and MG gratefully acknowledge support from the US National Science
Foundation Grant AST-1413610.  MB acknowledges additional support 
through New College and Oxford University's Balzan Fellowship as well as the University
of Minnesota Doctoral Dissertation Fellowship. Travel funding was supplied 
to MB, in part, by the University of Minnesota Thesis Research Travel Grant. CJL recognizes support from a grant from the Science \& Technology Facilities Council (ST/N003179/1). 
BDS acknowledges support from Balliol College, Oxford, and the National Aeronautics and Space Administration (NASA) through Einstein Postdoctoral Fellowship Award Number PF5-160143 issued by the Chandra X-ray Observatory Center, which is operated by the Smithsonian Astrophysical Observatory for and on behalf of NASA under contract NAS8-03060. The work of PJM is supported by the U.S. Department of Energy under contract number DE-AC02-76SF00515.

