%!TEX root = thesis.tex

\chapter{Measuring Nonparametric Morphological Diagnostics on SDSS Stamps}
\label{chap:3}


\section{Introduction}
Any machine classifier must have a set of features from which to learn to differentiate between classes. These features can be anything: pixel values, spectra, anything that can correlates well enough with the class boundary that the machine can learn that boundary. Choosing which features are most appropriate for each task is not necessarily straight-forward or easy. Too few features, and the machine will not be able to learn the things that define each class. Too many features and machine training time could increase substantially or, worse, training will be subjected to the Curse of Dimensionality: with increasing parameter space dimensionality, the number of samples required to learn that parameter space increases exponetially! 

In this work we draw on the Zurich Estimator of Structural Types (ZEST~\citep{Scarlata2007}). ZEST utilized five features measured from the light profile of galaxy imaging combined with a PCA analaysis to determine morphology for 120K COSMOS galaxies. These features are well known to correlate strongly with the distinction between early- and late-type galaxies. In this chapter we discuss how we measure these same features for the SDSS galaxy sample of GZ2. 

\section{Data}
We obtain $i$-band imaging from SDSS Data Release 12 for all XXX galaxies in the GZ2 project. [WHY $i$-band?]. 

Along with imaging, we also obtain basic SDSS measurements for each galaxy including the Petrosian radius. This value is used to create postage stamps from the SDSS fields for each galaxy with dimensions of 3 Petrosian radii where the galaxy of interest is centered on the stamp. Galaxies located within 3 Petrosian radii of the edge of a field were excluded as we did not perform mosaicing. This removed only XXX galaxies from our sample.

\section{Image Cleaning}
Because we seek to measure the galaxy's light profile, the existence of nearby galaxies will significantly hinder this endeavor. To mitigate this effect, postage stamps undergo a cleaning process. Sources in each stamp are identified with SExtractor \citep[ver. 2.8.6;][]{sextractor} and segmentation maps are created. From these, the galaxy light in pixels of nearby sources are replaced with values that correspond to the distribution of the background for that postage stamp. 

 GIVE EXAMPLES??  YES. 

 How many bad? How bad are the bad? What did I do to try to catch the bad? 

\section{Morphology Diagnostics}
Once the postage stamps have been cleaned of nearby galaxies, measurements of the light profile can commence. The first stage in this process is the measurement of the Petrosian radius. 
>>> PETROSIAN 1979

Compare my petro-rad to SDSS? --It doesn't look good. 

We use the Petrosian radius to define the aperture size for some of the following morphology measurements. [why did I measure my own instead of using SDSS??]

We compute the following widely adopted nonparametric measurements of the galaxy light distribution on the cleaned postage stamps:

Concentration is computed as $C = 5\log(r_{80}/ r_{20})$ where \rr{80} and \rr{20} are the
radii containing 80\% and 20\% of the galaxy light respectively.  Small values of this ratio 
tend to indicate disky galaxies, while larger values correlate with early-type ellipticals. 

Asymmetry quantifies the degree of rotational symmetry in the galaxy light distribution
 (not necessarily the physical shape of the galaxy as this parameter is not highly sensitive 
to low surface brightness features). A correction for background noise is applied (as in e.g.~\cite{Conselice2000}), i.e., 
\begin{equation}
A = \frac{\sum_{x,y} |I - I_{180}|}{ 2\sum|I|} - B_{180}
\end{equation}
where $I$ is the galaxy flux in each pixel $(x, y)$, $I_{180}$ is the image rotated by 180 degrees about the galaxy's central pixel, and $B_{180}$ is the average asymmetry of the background. 

The Gini coefficient, $G$,~\citep{Glasser1962, Abraham2003} describes how uniformly distributed a galaxy's flux is.  If $G$ is 0, the flux is distributed homogeneously among all galaxy pixels; if $G$ is 1,  the light is contained within a single pixel. This term correlates with $C$, however, $G$ does not require that the flux be in the central region of the galaxy.  We follow~\cite{Lotz2004} by first ordering the pixels by increasing flux value, and then computing
\begin{equation}
G = \frac{1}{|\bar X|n(n-1)}\sum_i^n(2i-n-1)|X_i|
\end{equation}
where $n$ is the number of pixels assigned to the galaxy, and $\bar X$ is the mean pixel value. 

\M{20}~\citep{Lotz2004} is the second order moment of the brightest 20\% of the galaxy flux. We compute it as
\begin{eqnarray}
 M_{tot} & = & \sum_i^nf_i[(x_i-x_c)^2 + (y_i-y_c)^2]  \\
 M_{20} & = & \log_{10} (\frac{\sum_iM_i}{M_{tot}}), ~~\textrm{while} \sum_ifi < 0.2f_{tot}
\end{eqnarray}
where M$_{tot}$, the total moment, is computed first and $f_{tot}$ is the total flux. For centrally concentrated objects, \M{20} correlates with $C$ but is also sensitive to bright off-centre knots of light. 

Finally, we use the ellipticity, $\epsilon = 1 - b/a$, of the light distribution as measured by SExtractor which computes the semi-major axis $a$ and semi-minor axis $b$ from the second-order moments of the galaxy light.  

In total, we measure morphological indicators for 282,350 SDSS galaxies. The relations between these diagnostics for the full sample is shown in the right panel of Figure~\ref{fig: morph thresh}. The code developed to clean and compute these morphology indicators is open source and can be found at \url{https://github.com/melaniebeck/measure_morphology}.



\section{Comparison with other samples}